### 2019-09-09 paper/paper.tex
conclusion

Figures~\ref{fig:sim}~and~\ref{fig:performance}  shows a snapshot of running workers exploiting the distributed library of Julia and the classification performance of each model, respectively. There are 8 workers running in parallel over 12 different machine learning classifiers. From the results, \emph{ExtraTree} from \emph{ScikitLearn} has the best performance with around 91.67\% accuracy followed by \emph{TreeBag} and \emph{SVMLinear} from \emph{Caret} library with 83.33 \% accuracy for both. With this workflow, it becomes trivial to search for optimal model by running them in parallel relying on \emph{Julia} to do the low-level tasks of scheduling, queueing, etc and making sure that compute resources are fairly optimised.

@@

datadir = joinpath("data/")
tsdata = extract_features_from_timeseries(datadir)

@@

\emph{TSML} main strength is the adoption of pipeline architecture containing filters and transformers to perform both preprocessing and modelling tasks. \emph{TSML}  exploits the following \emph{Julia} features: multiple dispatch, type inference, custom data types and abstraction, and parallel computations.  In addition, \emph{TSML} uses a common machine learning API for both internal and external ML libraries, distributed and threaded support for modeling, and a growing collection of filters for preprocessing and modeling. Extending \emph{TSML} can trivially be done by creating a custom data type filter and defining its corresponding \emph{fit} and \emph{transform} operations which the \emph{TSML} pipeline iteratively calls on its collection of filters.

>>>>

The data used in the experiment are sample snapshots of the data in our building operations. For reproducibility, the data can be found in the  \emph{juliacon2019-paper} branch of \emph{TSML} in \emph{Github}:  /data/benchmark/tsclassifier. There are four time series types, namely: AirOffTemp, Energy, Pressure, and RetTemp.  We  took a minimal number of samples and classes for discussion and demonstration purposes.

Figures~\ref{fig:sim}~and~\ref{fig:performance}  show a snapshot of running workers exploiting the distributed library of Julia and the classification performance of each model, respectively. There are 8 workers running in parallel over 12 different machine learning classifiers. From the results, \emph{ExtraTree} from \emph{ScikitLearn} has the best performance with 91.67\% accuracy followed by \emph{TreeBag} and \emph{SVMLinear} from \emph{Caret} library with 83.33 \% accuracy for both. With this workflow, it becomes trivial to search for optimal model by running them in parallel relying on \emph{Julia} to do the low-level tasks of scheduling, queueing, synchronizing, etc and making sure that dynamically available compute resources are fairly optimised.

@@

datadir = joinpath("tsdata/")
tsdata = extract_features_from_timeseries(datadir)

@@

\emph{TSML} main strength is the adoption of pipeline architecture containing filters and transformers to perform both preprocessing and modelling tasks. \emph{TSML}  exploits the following \emph{Julia} features: multiple dispatch, type inference, custom data types and abstraction, and parallel computations.  In addition, \emph{TSML} uses a common machine learning API for both internal and external ML libraries, distributed and threaded support for modeling, and a growing collection of filters for preprocessing, classification, clustering, and prediction. Extending \emph{TSML} can trivially be done by creating a custom data type filter and defining its corresponding \emph{fit} and \emph{transform} operations which the \emph{TSML} pipeline iteratively calls on its collection of filters.
